### 2013-05-17 report/reportmd.Rmd
Changed referencing to use .bib, added these to all folders
improve creation of knitr scripts
Initial from baad1. Removed bad line endings on csv files. Moved pdfs and all accessory friles to xtra folder for each data folder.

**Reference:** `r .dat$ref[2]`

@@

```{r echo=FALSE, fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
prepdata  <-  prepMapInfo(alldata$data, study)
drawWorldPlot (prepdata)
```

>>>>

**Reference:** `r formatBib(paste0("../", as.character(.dat$ref$reference)))[[1]]`

@@

```{r echo=FALSE, fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
prepdata  <-  prepMapInfo(alldata$data, .study)
drawWorldPlot (prepdata)
```
